The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-07-18 WavesData-2019/LatexNotes/notes.tex
NM

The statistical matching condition is
\begin{equation}
\meanup{\Hdn} = \meandn{\Hdn}
\end{equation}
An experimental observation is that the incoming skewness is small, $\meanup{H_3} \approx 0$. Inserting and simplifying gives
\begin{equation}
\label{H3H2}
\meandn{H_3} = \frac{C_2}{C_3} \dratdn^2 \,\, \Delta \mean{H_2}
\end{equation}
where $\Delta \mean{H_2} =  \meandn{H_2} - \meanup{H_2}$  indicates the difference between the upstream and downstream values.
To convert to dimensional, i.e.~experimental, values we note
\begin{align}
&\mean{u^3} =  \frac{\mean{\eta^3}} {\pi^{3/2} \mean{\eta^2}^{3/2}} = \pi^{-3/2} \skw(\eta) \\
&\mean{u_x^2} = \pi^{-1} \left(\frac{\lamupdn}{\etastd} \right)^2 \mean{\eta_x^2} 
= \pi^{-1} \left(\frac{\lamupdn}{\etastd} \right)^2 \var(\eta_x)
\end{align}
Therefore
\begin{align}
& \meandn{H_3} = \frac{\pi}{3} \mean{u^3} = 
\frac{1}{3} \pi^{-1/2} \skwdn(\eta) \\
& \meanupdn{H_2} = \pi \meanupdn{u_x^2} = 
\left(\frac{\lamupdn}{\etastd} \right)^2 \var(\eta_x)
\end{align}
The second equation implies
\begin{equation}
\Delta \mean{H_2} =  \meandn{H_2} - \meanup{H_2} = 
\etastd^{-2} \left( \lamdn^2 \vardn(\eta_x) - \lamup^2 \varup(\eta_x) \right) =
\etastd^{-2} \Delta \left( \lam^2 \var(\eta_x) \right)
\end{equation}
Then \eqref{H3H2} gives the relationship
\begin{equation}
\frac{\skw(\eta)} {\Delta \left( \lam^2 \var(\eta_x) \right) } =
\frac{3 \pi^{1/2} C_2 \dratdn^2}{C_3 \etastd^2}  =
\frac{\pi^2}{3 \lamfac^2} \delup^2 \epsup^{-1} \etastd^{-2} \dratdn^2 =
\frac{\pi^2}{3 \lamfac^2} \lamup^{-2} \epsup^{-3} \dratdn^2
\end{equation}
Performing some additional manipulations, and noting that $(\lamdn/\lamup)^2 = \ddn/\dup = \dratdn$, gives
\begin{equation}
\frac{\skwdn(\eta)} {\dratdn \vardn(\eta_x) - \varup(\eta_x)} = 
\frac{\pi^2}{3 \lamfac^2} \epsup^{-3} \dratdn^2
\end{equation}
In particular, the ratio on the left, which can be measured in the experiments, is predicted to scale as the inverse cube of the wave amplitude and as the square of the depth ratio.

>>>>

The statistical matching condition is
\begin{equation}
\meanup{\Hdn} = \meandn{\Hdn}
\end{equation}
An experimental observation is that the incoming skewness is small, $\meanup{H_3} \approx 0$. Inserting and simplifying gives
\begin{equation}
\label{H3H2}
\frac{\meandn{H_3}} {\meandn{H_2} - \meanup{H_2}} = \frac{C_2}{C_3} \dratdn^2
\end{equation}
%where $\Delta \mean{H_2} =  \meandn{H_2} - \meanup{H_2}$  indicates the difference between the upstream and downstream values.
To convert to dimensional, i.e.~experimental, values we first note that
\begin{align}
\mean{H_3} = \frac{\pi}{3} \mean{u^3} = 
\frac{1}{3} \pi^{-1/2} \frac{\mean{\eta^3}}{\etastd^3} = \frac{1}{3} \pi^{-1/2} \skw(\eta)
\end{align}
Second, to convert the surface slope, we note
\begin{align}
\pd{u}{\tilde{x}} = \frac{\lamfac \lam}{\pi^{3/2} \etastd} \pd{\eta}{\xi}
\end{align}
where slope with respect to $\xi$ is the same as with respect to dimensional $x$.
Hence, we have
\begin{align}
&\mean{H_2} = \pi \mean{ \left( \pd{u}{\tilde{x}} \right)^2} = 
\left( \frac{\lamfac \lam}{\pi \etastd} \right)^2 \var(\eta_x)
\end{align}
Algebra gives
\begin{equation}
\frac{\meandn{H_3}} {\meandn{H_2} - \meanup{H_2}} = 
\frac{\pi^{3/2}} {3 \lamfac^2 \etastd^2} 
\left( \frac{\skwdn(\eta)}{ \lamdn^2 \vardn(\eta_x) - \lamup^2 \varup(\eta_x)} \right) = 
\frac{\pi^{3/2}} {3 \lamfac^2 \etastd^2 \lamup^2} 
\left( \frac{\skwdn(\eta)} {\dratdn \vardn(\eta_x) - \varup(\eta_x)} \right)
\end{equation}
where in the second equality, we have used the fact that
\begin{equation}
\frac{\lamdn^2}{\lamup^2} = \frac{\ddn}{\dup} = \dratdn
\end{equation}

\vsp{5}

Then \eqref{H3H2} gives the relationship
\begin{equation}
\frac{\skw(\eta)} {\Delta \left( \lam^2 \var(\eta_x) \right) } =
\frac{3 \pi^{1/2} C_2 \dratdn^2}{C_3 \etastd^2}  =
\frac{\pi^2}{3 \lamfac^2} \delup^2 \epsup^{-1} \etastd^{-2} \dratdn^2 =
\frac{\pi^2}{3 \lamfac^2} \lamup^{-2} \epsup^{-3} \dratdn^2
\end{equation}
Performing some additional manipulations, and noting that $(\lamdn/\lamup)^2 = \ddn/\dup = \dratdn$, gives
\begin{equation}
\frac{\skwdn(\eta)} {\dratdn \vardn(\eta_x) - \varup(\eta_x)} = 
\frac{\pi^2}{3 \lamfac^2} \epsup^{-3} \dratdn^2
\end{equation}
In particular, the ratio on the left, which can be measured in the experiments, is predicted to scale as the inverse cube of the wave amplitude and as the square of the depth ratio.
